How to Learn Useful Changes to Software Projects\\(to Reduce Runtimes and Software Defects)

### 2015-08-28 Manuscript.tex
Updates from ShareLaTeX

\definecolor{Code}{rgb}{0,0,0}
\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
\definecolor{Numbers}{rgb}{0.5,0,0}
\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
\definecolor{Keywords}{rgb}{0,0,1}
\definecolor{self}{rgb}{0,0,0}
\definecolor{Strings}{rgb}{0,0.63,0}
\definecolor{Comments}{rgb}{0,0.63,1}
\definecolor{Comments}{rgb}{0.5,0.5,0.5}
\definecolor{Backquotes}{rgb}{0,0,0}
\definecolor{Classname}{rgb}{0,0,0}
\definecolor{FunctionName}{rgb}{0,0,0}
\definecolor{Operators}{rgb}{0,0,0}
\definecolor{Background}{rgb}{1,1,1}

 \definecolor{lavenderpink}{rgb}{0.98, 0.68, 0.82}
 \definecolor{celadon}{rgb}{0.67, 0.88, 0.69}
\newcommand{\G}{\cellcolor{green}}
\newcommand{\Y}{\cellcolor{yellow}}

@@

Using data from 11 software projects,  XTREE found   larger reductions that three
alternate methods.  Those reductions had 
median size of (55\%,38.5\%) and   largest size of (78\%,94\%) in
(defects,runtimes), respectively.
\end{abstract}
\section{Introduction}
Business users are demanding  tools that support    business-level interpretations of their data. At a panel on software analytics at ICSE`12, industrial practitioners lamented the state of the art in software analytics~\cite{menzies12a}. Panelists commented  ``prediction is all well and good, but what about decision making?''. Note that these panelists were more interested in the interpretations and follow-up that occurs after the mining, rather than just the mining itself. So:
\bi
\item
Instead of just accepting {\em predictions} on how many software defects to expect, business users might now demand a {\em plan} to reduce the likelihood of those defects.
\item
Instead of just accepting {\em predictions} on the runtime time of their software, business users might now demand a {\em plan} to reduce that runtime. 
\ei
In response to this business-level demands for planners,
we propose a novel {\em planning} method called XTREE for learning changes to a software system
such that its performance ``improves'', according to some measure. This paper uses XTREE
to reduce  the expected value of the
defects     in Jureczko et al.'s    JAVA systems~\cite{jureczko10};
and the runtimes   in   software    configured by  Siegmund et al.~\cite{sven12}.

@@

Note that we make no assumption that a plan mentions every features
(so plan1 can be  more succinct than plan2 when plan1  mentions fewer features than
plan2).

@@

This paper is about the next step {\em after} prediction. Suppose
a business user is presented with  a prediction and they do not like what they see; e.g. the runtimes are too long of the number of defects is too high. This user may
then ask a {\em planning}  question; i.e. ``what can we change to do better than that?''.

@@

One way to propose changes to a project would be to   ask some smart experienced
person for their opinion on how to (e.g.) reduce defects and/or decrease runtimes. Sometimes
such advice 
is an effective strategy and sometimes it is not.
According to Passos et al.~\cite{passos11},  developers
may  assume that the lessons they learn from a few past
projects are general to 
all their future projects. They comment ``past experiences were taken into account without 
much consideration for their context~\cite{passos11}.  
 J{\o}rgensen \& Gruschke~\cite{jorgensen09} offer  a similar warning. They report that 
  supposed software engineering    ``gurus'' rarely use lessons
  from past projects to improve their future reasoning and that such poor
  past advice can be detrimental to new projects.~\cite{jorgensen09}.
  Accordingly, we   propose a ``trust, but verify'' approach.
  After a software guru offers some sage wisdom,  it is wise to ask some other oracle 
  if there are any better options
  (just as a sanity check).
  The rest of this paper discusses some methods to build automatic oracles 
  to implement that   sanity check.

Another way  to find   changes to a project
might be to rely
on the peer review processes used by the 
SE research community. This approach would propose changes to software
projects that concur with internationally accept best practices. 
There are two
problems with that approach. Firstly, given the rapid pace of change in software
engineering, we may be asking questions for which there is no currently accept
``best practice''. For example, only very recently has there been any work
of predicting software runtimes based on choices within Makefiles. While the work
of Siegmund et al.~\cite{sven12} is certainly state of the art, it does
cannot yet represent ``internationally accept best practices'' since that work is so
recent.

Secondly, given the diversity of SE products and practices
and personnel, it may well be that the current project being discussed is 
substantively different to prior work. 
Numerous recent {\em local learning} results compare (1) single models
learned from all available data to (2) multiple models learned from clusters within the data~\cite{betten14,yang11,yang13,minku13,me12d,me11m,posnett11}.
A repeated result in those studies in that the local models generated the better effort
and defect predictions (better median results,
lower variance in the predictions). \tion{surprise} of this  paper offers yet another locality result:
\bi
\item
One standard rule in the literature
is that it is useful to implement modules such that they are internally cohesive (use
much of their own local methods) while being loosely coupled with other classes~\cite{Dhama199565}.
\item
While that may be true in general, for particular classes other changes may be more important
(later in this paper, we show one set of results were that is indeed the case).
\ei
In summary, 
it is useful to have automatic methods to recommend changes. Such
methods can fill in for human gurus (if such gurus are absent) or 
to offer a second opinion.
Also, prior to making automatic recommendations, it is wise to first stratify the data
(clump it into related examples) then generate advice specific to each clump.
Accordingly, the rest of this paper defines and evaluates
automatic methods to find plans from
  $N$ examples divided  into  many clumps.

@@

To answer this question, we note
that data miners explore two  ``clouds'' of data: (1) the cloud of training examples and (2) the  cloud   of test examples
(for a visualization of these clouds, see \fig{howxy}).
\begin{figure}[!t]
  \includegraphics[width=\linewidth]{figs/twodee.eps} 
 % \includegraphics[width=1\linewidth]{figs/BDBC.eps}
\caption{Gray, red, green show (1) training examples, (2) test examples and 
  (3) tests that have been altered by planners.
  This figure uses axes generated from the first two components of a PCA analysis of all points. 
}\label{fig:howxy}
\end{figure}
We should mistrust the predictions made by a  model   if it is being applied to examples  that are
too far away from the
training cloud.
To test for ``too far'', we can run a data mining experiment that tests how well
a model learned from the training data applies to the test data. Such experiments return some performance value.

Note that predictions  about changes that  fall within the space of the training+test data, will be at least
as reliable as the performance value found in the above data mining experiment.
Given this, one thing  can be asserted about predictions on changed examples:
\bi
\item Predictions for changes that move examples towards/away from the training data can be trusted more/less (respectively).
\ei  
Accordingly, we should use  {\em trust-increasing} planners that generate changed examples {\em closer} to the
training examples.  To see how this works, 
 \fig{howxy} is from the {\em ivy} data
set, which is one of the Jureczko data sets explored in this paper. It shows: (1)~the training examples in gray, (2)~the test examples in red, and (3)~the
changed  examples displaced after applying a plan (in green).
 Note that the  the   changed examples
cases  (shown in green)  fall closer to the training cases (shown in gray) than
the test cases (shown in red).

In that green region of changed examples, our belief in the value of predictions
will be as much (or more) as our belief in the value of the predictions in the red region (that
contains the original test data).
This pattern of \fig{howxy} (where the changes examples are found closer to  the training cases than the test cases) has been observed in all the other data sets studied in this
paper. Hence,  we can assert that
predictors learned from these training examples have some authority in the regions
contain the changes examples.

That said, the above comes with some important caveats:
\bi
\item 
The quality of the prediction depends on the nature of the training data. Thus, we strongly recommend that both data set and the predictor be assessed prior to planning. This ensures that the predictor's performance is adequate for a data set. We tackle this issue in detail in \tion{tesd}.
\item
Planners should be designed to be {\em trust increasing}. We list four such planning methods in \tion{planners}.
\item
Where possible, planners should be assessed via some external
oracle that can accurately assess new examples. For an example of that kind of analysis,
see  \tion{coc}.
\ei

@@

 \section{Test Data}\label{sect:tesd}
To assess our planning methods, we use data from Jureczko et al.'s object-oriented JAVA systems~\cite{jureczko10}  and
  software system   configuration data from by  Siegmund et al.~\cite{sven12}.
  See github.com/ai-se/XTREE\#data for full access to this data.

   The Jurecko data records number of known defects for each class using a post-release bug tracking system. The classes are described in terms of
  nearly two dozen metrics such as number of children, lines of code, etc. For details on the Jurecko data, see  \fig{ck} and \fig{jd}. 
 All the planning methods of this paper reflect on the numeric value of the raw defect counts. The predictor considers defects to be a discrete class data set,where defects are \textit{\texttt{TRUE}} if the numeric defect count is greater than zero and \textit{\texttt{FALSE}} otherwise.

  The Siegmund data, described in \fig{cpm},  records  the runtimes of compiled systems. To make that data, Siegmund et al. perturbed
  the configuration parameters in the Makefiles of six systems: Apache, SQLite, LLVM, x264 and two versions of the
  Berkeley database (one written in ``C'' and one in Java). Then, the performance was measured using standard benchmarking tools (delivered by \textsc{Oracle} for Berkley data sets and other popular tools such as \textsc{autobench} and \textsc{httpref} for the rest)~\cite{sven12}. It's worth noting that in each of the above data set, some configurations are interdependent, this is expressed using a \textit{feature model}.
   \fig{bdbc} shows an example of such a feature model defining valid combinations of settings to on the Berkley database (``C'' version). These feature models were used by Siegmund et al. to ensure all their perturbations are valid
   (we will use the same models to cull invalid plans).

@@

  Our evaluation strategy (discussed below) divides this data into a training a test set.
  From the train set we apply a data miner (to learn a quality predictor) and
  various planning methods (to learn different plans). Next, we try applying
  each of those plans to the  test set and ask the quality predictor to assess the changed examples.
  Finally, we say that the  ``best'' planner is the one that most reduces the predicted values
  in the changed examples.

  As mentioned in the last section,  this approach depends on having effective predictors for assessing the results.
  For the Siegmind data, this criteria was   relatively easy to achieve.
  The data in those data sets have a continuous class (runtime of the compiled system)
  so the performance of a quality predictor can  be measured in terms of  difference between the predicted runtime $p$ of test case items and their actual runtimes $a$ using  $s= 1 - \frac{abs(a - p)}{a}$ (and {\em higher} values are {\em better}).
This paper  explores six Siegmund configuration data sets:  Berkeley DB (Java and C versions), Apache, SQLite, LLVM, and
  x264. 
  As a preliminary study, we split that data   into equal sized train:test groups
  and trained a Random Forest
  Regressor (from the SciKit learn kit~\cite{Pedregosa2012})   on one half, then applied to the other. This  achieved nearly perfect scores of $s=\{99.9, 99.8, 99.4, 99.1, 96.1\}\%$.
That is, we can be very confident that the predictors from the Siegmund data can assess
our plans. (Aside: if the reader doubts that such high scores are achievable, we note that these scores are consistent with those achieved by predictors built by Siegmund et al.~\cite{sven12}.)

@@

 \fig{j} shows our preliminary studies with the Jureczko   data.
Given access to $V$ released
versions, we test on version $V$ and train on the available data from $V-1$ earlier releases (as
shown in \fig{j}, this means that we are training on hundreds to thousands
of classes and testing on smaller test suites).
Note the   \colorbox{lavenderpink}{three bottom rows}   marked with $\times$: these contain predominately defective classes (two-thirds, or more).  In such data sets, it is hard to distinguish good from bad (since there are so many bad examples).

The  Jureczko data uses non-numeric discrete classes (``defective'' or ``not'').
For such data, quality predictor   is be measured using
(1) the  probability of detection (a.k.a. ``pd'' or recall):  the percent of faulty classes in
the test data detected
by the {\em predictor}; and (2) the 
probability of false alarm (a.k.a. ``pf''): the percent of non-fault
classes that are {\em predicted} to be defective.

As a preliminary study, we split the Jureczko  data into train and test groups.
Random Forests (again, from the SciKit learn kit~\cite{Pedregosa2012}) were
built from the training data, then applied to the test data.
The ``untuned'' columns of \fig{j} shows those results. We called a data set ``usable'' if Random Forest was able to classify majority of the instances correctly. For this purpose, we set a threshold of $\mathit{pd}\ge 60 \wedge \mathit{pf} \le 30$\% to select these data sets. With this threshold, however, none of our data sets were be suitable for this study.

Fortunately, the ``tuned'' columns of \fig{j} show that we can salvage some of the data sets. Pelayo and Dick~\cite{pelayo07} report that defect prediction is improved by SMOTE~\cite{Chawla2002}; i.e. an over-sampling of minority-class examples and under-sampling of majority-class examples. Also, Fu et al.~\cite{fu:ase15} report that parameter tuning with differential evolution~\cite{storn97} can quickly explore the tuning options of Random Forest to find better settings for the (e.g.) size of the forest, the termination criteria
for tree generation, etc. The rows \colorbox{celadon}{marked with a $\star$} in \fig{j} show data sets whose performance was improved remarkably by these techniques. For example, in {\em poi}, the recall increased by 4\% while the false alarm rate dropped by 21\%. However,  as might have been expected, we could not salvage the data sets in the  three bottom rows.

@@

That said, we have taken care to document in this paper the decisions made by engineering
judgement that could effect our conclusions. The above code used a set of variables which future
work should vary in order to test the internal validity of our conclusions:
\bi
\item All our planners divide data into groups of size $\alpha=\sqrt{N}$
\item Method2 used the top $\beta=33\%$ most informative features (ranked using INFOGAIN);
\item Method3 uses a fraction $F=0.5$ to compute the plan from the delta;
\item Method4 (XTREE) assumed that another sibling was useful if  had 
 a  score less than $\gamma=0.5$ times the mean score of the current leaf.
 \ei

>>>>

\definecolor{Code}{rgb}{0,0,0}
\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
\definecolor{Numbers}{rgb}{0.5,0,0}
\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
\definecolor{Keywords}{rgb}{0,0,1}
\definecolor{self}{rgb}{0,0,0}
\definecolor{Strings}{rgb}{0,0.63,0}
\definecolor{Comments}{rgb}{0,0.63,1}
\definecolor{Comments}{rgb}{0.5,0.5,0.5}
\definecolor{Backquotes}{rgb}{0,0,0}
\definecolor{Classname}{rgb}{0,0,0}
\definecolor{FunctionName}{rgb}{0,0,0}
\definecolor{Operators}{rgb}{0,0,0}
\definecolor{Background}{rgb}{1,1,1}
\bibliographystyle{unsrt}
 \definecolor{lavenderpink}{rgb}{0.98, 0.68, 0.82}
 \definecolor{celadon}{rgb}{0.67, 0.88, 0.69}
\newcommand{\G}{\cellcolor{green}}
\newcommand{\Y}{\cellcolor{yellow}}

@@

Using data from 11 software projects,  XTREE found   larger reductions than three
alternate methods.  Those reductions had 
median size of (56\%,28\%) and   largest size of (60\%,77\%) in
(defects,runtimes), respectively.
\end{abstract}
\section{Introduction}
Business users are demanding  tools that support    business-level interpretations of their data. At a panel on software analytics at ICSE`12, industrial practitioners lamented the state of the art in software analytics~\cite{menzies12a}. Panelists commented  ``prediction is all well and good, but what about decision making?''. Note that these panelists were more interested in the interpretations and follow-up that occurs after the mining, rather than just the mining itself. So:
\bi
\item
Instead of just accepting {\em predictions} on how many software defects to expect, business users might now demand a {\em plan} to reduce the likelihood of those defects.
\item
Instead of just accepting {\em predictions} on the runtime time of their software, business users might now demand a {\em plan} to reduce that runtime. 
\ei
In response to this business-level demands for planners,
we propose a novel {\em planning} method called XTREE for learning changes to a software system
such that its performance ``improves'', according to some measure. This paper uses XTREE
to reduce  the expected value of the
defects     in Jureczko et al.'s    JAVA systems~\cite{jureczko10};
and the runtimes   in   software    configured by  Siegmund et al.~\cite{sven12}.

@@

Note that we make no assumption that a plan mentions every feature
(so plan1 can be  more succinct than plan2 when plan1  mentions fewer features than
plan2).

@@

This paper is about the next step {\em after} prediction. Suppose
a business user is presented with  a prediction and they do not like what they see; e.g. the runtimes are too long or the number of defects is too high. This user may
then ask a {\em planning}  question; i.e. ``what can we change to do better than that?''.

@@

One way to propose changes to a project would be to   ask some smart experienced
person for their opinion on how to (e.g.) reduce defects and/or decrease runtimes. Sometimes
such advice 
is an effective strategy and sometimes it is not.
According to Passos et al.~\cite{passos11},  developers
may  assume that the lessons they learn from a few past
projects are general to 
all their future projects. They comment ``past experiences were taken into account without 
much consideration for their context''~\cite{passos11}.  
 J{\o}rgensen \& Gruschke~\cite{jorgensen09} offer  a similar warning. They report that 
  supposed software engineering    ``Gurus'' rarely use lessons
  from past projects to improve their future reasoning and that such poor
  past advice can be detrimental to new projects.~\cite{jorgensen09}.
  Accordingly, we   propose a ``trust, but verify'' approach.
  After a software guru offers some sage wisdom,  it is wise to ask some other oracle 
  if there are any better options
  (just as a sanity check).
  The rest of this paper discusses some methods to build automatic oracles 
  to implement that   sanity check.

Another way  to find   changes to a project
might be to rely
on the peer review processes used by the 
SE research community. This approach would propose changes to software
projects that concur with internationally accept best practices. 
There are two
problems with that approach. Firstly, given the rapid pace of change in software
engineering, we may be asking questions for which there is no currently acceptable
``best practice''. For example, only very recently has there been any work
of predicting software runtimes based on choices within Makefiles. While the work
of Siegmund et al.~\cite{sven12} is certainly state of the art, it does not yet represent ``internationally accept best practices'' since that work is so
recent.

Secondly, given the diversity of SE products and practices
and personnel, it may well be that the current project being discussed is 
substantively different to prior work. 
Numerous recent {\em local learning} results compare (1) single models
learned from all available data to (2) multiple models learned from clusters within the data~\cite{betten14,yang11,yang13,minku13,me12d,me11m,posnett11}.
A repeated result in those studies is that the local models generated better effort
and defect predictions (better median results,
lower variance in the predictions). \tion{surprise} of this  paper offers yet another locality result:
\bi
\item
One standard rule in the literature
is that it is useful to implement modules such that they are internally cohesive (use
much of their own local methods) while being loosely coupled with other classes~\cite{Dhama199565}.
\item
While that may be true in general, for particular classes other changes may be more important
(later in this paper, we show one set of results where that is indeed the case).
\ei
In summary, 
it is useful to have automatic methods to recommend changes. Such
methods can fill in for human gurus (if such Gurus are absent) or 
to offer a second opinion.
Also, prior to making automatic recommendations, it is wise to first stratify the data
(clump it into related examples) then generate advice specific to each clump.
Accordingly, the rest of this paper defines and evaluates
automatic methods to find plans from
  $N$ examples divided  into  many clumps.

@@

To answer this question, we note
that data miners explore two  ``clouds'' of data: (1) the cloud of training examples and (2) the  cloud   of test examples
(for a visualization of these clouds, see \fig{howxy}).
\begin{figure}[!t]
  \includegraphics[width=\linewidth]{figs/2d.eps} 
 % \includegraphics[width=1\linewidth]{figs/BDBC.eps}
\caption{Gray, red, green show (1) training examples, (2) test examples and 
  (3) tests that have been altered by planners.
  This figure uses axes generated from the first two components of a PCA analysis of all points. 
}\label{fig:howxy}
\end{figure}
We should mistrust the predictions made by a  model   if it is being applied to examples  that are
too far away from the
training cloud.
To test for ``too far'', we can run a data mining experiment that tests how well
a model learned from the training data applies to the test data. Such experiments return some performance value.

Note that predictions  about changes that  fall within the space of the training+test data, will be at least
as accurate as the predictions of the original test data. With this, we assert that the predictions for changes that move examples towards/away from the training data can be trusted more/less (respectively).

Accordingly, we should use {\em trust-increasing} planners that generate changed examples {\em closer} to the
training examples.  To see how this works, 
 \fig{howxy} is from the {\em ivy} data
set, which is one of the Jureczko data sets explored in this paper. It shows: (1)~the training examples in gray, (2)~the test examples in red, and (3)~the
changed  examples displaced after applying a plan (in green).
 Note that the  the   changed examples
cases  (shown in green)  fall closer to the training cases (shown in gray) than
the test cases (shown in red).

In that green region of changed examples, our belief in the value of predictions
will be as much, if not more than our belief in the value of the predictions in the red region (that
contains the original test data).
This pattern of \fig{howxy} (where the examples are found closer to  the training cases than the test cases) has been observed in all the other data sets studied in this
paper. Hence,  we can assert that
predictors learned from these training examples have some authority in the regions
containing the changes examples.

That said, the above comes with some important caveats:
\bi
\item 
The quality of the prediction depends on the nature of the training data. Thus, we strongly recommend that both the data set and the predictor be assessed prior to planning. This ensures that the predictor's performance is adequate for a data set. We tackle this issue in detail in \tion{tesd}.
\item
Planners should be designed to be {\em trust increasing}. We list four such planning methods in \tion{planners}.
\item
Where possible, planners should be assessed via some external
oracle that can accurately assess new examples. For an example of that kind of analysis,
see  \tion{coc}.
\ei

@@

 \section{Test Data}\label{sect:tesd}
To assess our planning methods, we use data from Jureczko et al.'s object-oriented JAVA systems~\cite{jureczko10}  and
  software system   configuration data from by  Siegmund et al.~\cite{sven12}\footnote{ See \url{http://git.io/vGYxc} for full access to this data.}.

   The Jureczko data records number of known defects for each class using a post-release bug tracking system. The classes are described in terms of
  nearly two dozen metrics such as number of children (noc), lines of code (loc), etc. For details on the Jureczko data, see  \fig{ck} and \fig{jd}. 
 All the planning methods of this paper reflect on the numeric value of the raw defect counts. The predictor considers defects to a Boolean class data set, where defects are \texttt{TRUE} if the numeric defect count is greater than zero and \texttt{FALSE} otherwise.

  The Siegmund data, described in \fig{cpm},  records  the runtimes of compiled systems. To obtain the  data, Siegmund et al. perturbed
  the configuration parameters in the Makefiles of six systems: Apache, SQLite, LLVM, x264 and two versions of the
  Berkeley database (one written in ``C'' and one in Java). Then, the performance was measured using standard benchmarking tools (delivered by \textsc{Oracle} for Berkley data sets and other popular tools such as \textsc{autobench} and \textsc{httpref} for the rest)~\cite{sven12}. It's worth noting that in each of the above data set, several configurations are interdependent, this is expressed using a \textit{feature model}.
   \fig{bdbc} shows an example of such a feature model defining valid combinations of settings in the Berkley database (``C'' version). These feature models were used by Siegmund et al. to ensure all their perturbations are valid
   (we will use the same models to cull invalid plans).

@@

  Our evaluation strategy (discussed below) divides this data into a training and a test set.
  From the train set we apply a data miner (to learn a quality predictor) and
  various planning methods (to learn different plans). Next, we try applying
  each of those plans to the  test set and ask the quality predictor to assess the changed examples.
  Finally, we say that the  ``best'' planner is the one that most reduces the predicted values
  in the changed examples.

  As mentioned in the last section,  this approach depends on having effective predictors for assessing the results.
  For the Siegmund data, this criteria was   relatively easy to achieve.
  The data in those data sets have a continuous class (runtime of the compiled system)
  so the performance of a quality predictor can  be measured in terms of  difference between the predicted runtime $p$ of test case items and their actual runtimes $a$ using  $s= (1 - \frac{abs(a - p)}{a})\times100\%$ ({\em higher} values are {\em better}).
This paper  explores six Siegmund configuration data sets:  Berkeley DB (Java and C versions), Apache, SQLite, LLVM, and
  x264. 
  As a preliminary study, we split that data into equal sized train:test groups
  and trained a Random Forest
  Regressor (from the SciKit learn kit~\cite{Pedregosa2012})   on one half, then applied to the other. After repeating this process 40 times, we achieved nearly perfect accuracy of $s=\{99.9, 99.8, 99.4, 99.1, 96.1\}\%$.
Therefore, we can be very confident that the predictors from the Siegmund data can assess
our plans. (Aside: if the reader doubts that such high scores are achievable, we note that these scores are consistent with those achieved by predictors built by Siegmund et al.~\cite{sven12}.)

@@

 \fig{j} shows our preliminary studies with the Jureczko   data.
Given access to $V$ released
versions, we test on version $V$ and train on the available data from $V-1$ earlier releases (as
shown in \fig{j}, this means that we are training on hundreds to thousands
of classes and testing on smaller test suites).
Note the   \colorbox{lavenderpink}{three bottom} \colorbox{lavenderpink}{rows}   marked with $\times$: these contain predominately defective classes (two-thirds, or more).  In such data sets, it is hard to distinguish good from bad (since there are so many bad examples).

In order to identify the presence (or absence) of defects, we can consider using Boolean classes in the  Jureczko data ( \texttt{True} if defects $\gt$ 0; \texttt{False} if defects = 0).
For such data, quality predictor   is be measured using
(1) the  probability of detection (a.k.a. ``pd'' or recall):  the percent of faulty classes in
the test data detected
by the {\em predictor}; and (2) the 
probability of false alarm (a.k.a. ``pf''): the percent of non-fault
classes that are {\em predicted} to be defective.

As a preliminary study, we split the Jureczko  data into train and test groups.
Random Forests (again, from the SciKit learn kit~\cite{Pedregosa2012}) were
built from the training data, then applied to the test data.
The ``untuned'' columns of \fig{j} shows those results. We called a data set ``usable'' if Random Forest was able to classify majority of the instances correctly. For this purpose, we set a threshold of $\mathit{pd}\ge 60 \wedge \mathit{pf} \le 30$\% to select suitable data sets. With this threshold, however, none of our data sets were be suitable for this study.

Fortunately, the ``tuned'' columns of \fig{j} show that we can salvage some of the data sets. Pelayo and Dick~\cite{pelayo07} report that defect prediction is improved by SMOTE~\cite{Chawla2002}; i.e. an over-sampling of minority-class examples and an under-sampling of majority-class examples. Also, Fu et al.~\cite{fu:ase15} report that parameter tuning with differential evolution~\cite{storn97} can quickly explore the tuning options of Random Forest to find better settings for the (e.g.) size of the forest, the termination criteria
for tree generation, etc. The rows \colorbox{celadon}{marked with a $\star$} in \fig{j} show data sets whose performance was improved remarkably by these techniques. For example, in {\em poi}, the recall increased by 4\% while the false alarm rate dropped by 21\%. However,  as might have been expected, we could not salvage the data sets in the  three bottom rows.

@@

That said, we have taken care to document in this paper the decisions made by engineering
judgement that could effect our conclusions. The above code used a set of variables which future
work should vary in order to test the internal validity of our conclusions:
\bi
\item All our planners divide data into groups of size $\alpha=\sqrt{N}$
\item Method2 used the top $\beta=33\%$ most informative features (ranked using INFOGAIN);
\item Method3 uses a fraction $F=0.5$ to compute the plan from the delta;
\item XTREE considered a sibling useful if it's score was less than $\gamma=0.5$ times the mean score of the current leaf.
 \ei
